---
title: "test site"
output: html_document
date: "2024-04-16"
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(dplyr)
library(ggplot2)
```


# The Data:
 - load and clean the data
 - add column to indicate streaming platform
 - remove unwanted data 'id', and 'imdb_id'
 - reorganize column
```{r, echo=FALSE}
# add column to indicate streaming platform

netflix = read_csv("netflix_titles.csv", show_col_types = FALSE)
hbo = read_csv("hbo_titles.csv", show_col_types = FALSE)
amazon = read_csv("amazon_titles.csv", show_col_types = FALSE)
disney = read_csv("disney_titles.csv", show_col_types = FALSE)
apple = read_csv("apple_titles.csv", show_col_types = FALSE)

# remove unwanted data 'id', and 'imdb_id'

netflix = netflix %>% subset(select = -c(id, imdb_id))
amazon = amazon %>% subset(select = -c(id, imdb_id))
apple = apple %>% subset(select = -c(id, imdb_id))
hbo = hbo %>% subset(select = -c(id, imdb_id))
disney = disney %>% subset(select = -c(id, imdb_id))

# add column to show show streaming platforms and reorganize columns

netflix = netflix %>% mutate(platform = 'Netflix') %>% select(platform, everything())
disney = disney %>% mutate(platform = 'Disney') %>% select(platform, everything())
hbo = hbo %>% mutate(platform = 'HBO Max') %>% select(platform, everything())
apple = apple %>% mutate(platform = 'Apple TV') %>% select(platform, everything())
amazon = amazon %>% mutate(platform = 'Amazon') %>% select(platform, everything())  
```
# combine
 - all data sets as one : all_titles
 - date for just movies : all_movies
 - data for just shows  : all_shows
```{r, echo=FALSE}

all_titles = full_join(netflix, amazon) %>% full_join(apple) %>% full_join(disney) %>% full_join(hbo)

all_movies = all_titles %>% filter(type == 'MOVIE')

all_shows = all_titles %>% filter(type == 'SHOW')
```


## shows vs movies
 - looking at the amount of movies and shows in the data sets

```{r pressure, echo=FALSE}
#shows percentages of all shows and movies between all platforms 
all_titles %>% 
  group_by(platform, type) %>% summarise(percent = 100 * n() / nrow(all_titles), total = n(), .groups = 'drop')

ggplot(all_titles) + aes(platform, fill = type) + geom_bar(position = 'dodge')+ geom_text(stat='count',  aes(label = stat(count),group=type), position=position_dodge(1))


#shows percentage of total items streamed between all platforms
all_titles %>% 
  group_by(platform) %>% summarise(percent = 100 * n() / nrow(all_titles), total = n())

#probably not needed
text(barplot(table(all_titles$platform), ylim = c(0, max(table(all_titles$platform)) * 1.1)),
     table(all_titles$platform),
     labels = table(all_titles$platform),
     pos = 3 ,cex = 0.8, col = "blue")


#shows the percentages of ratios to movies without regard for platform
all_titles %>% 
  group_by(type) %>% summarise(percent = 100 * n() / nrow(all_titles), total = n())


#probably not needed
text(barplot(table(all_titles$type), ylim = c(0, max(table(all_titles$type)) * 1.1)),
     table(all_titles$type),
     labels = table(all_titles$type), pos = 3 ,cex = 0.8, col = "blue")
```


```{r pressure, echo=FALSE}
#shows the ratio of movies to shows for each separate platform in one table
all_totals = full_join(disney %>% 
                         group_by(platform, type) %>% summarise(percent = 100 * n() / nrow(disney), total = n(), .groups = 'drop'),
                       netflix %>% 
                         group_by(platform, type) %>% summarise(percent = 100 * n() / nrow(netflix), total = n(), .groups = 'drop'))
all_totals = full_join(all_totals, hbo %>% group_by(platform,type) %>% summarise(percent = 100 * n() / nrow(hbo), total = n(), .groups = 'drop'))
all_totals = full_join(all_totals, amazon %>% group_by(platform,type) %>% summarise(percent = 100 * n() / nrow(amazon), total = n(), .groups = 'drop'))
all_totals = full_join(all_totals, apple %>% group_by(platform,type) %>% summarise(percent = 100 * n() / nrow(apple), total = n(), .groups = 'drop'))
all_totals  


#shows ratio of movies to shows

disney %>% 
  group_by(type) %>% summarise(percent = 100 * n() / nrow(disney), total = n())
netflix %>% 
  group_by(type) %>% summarise(percent = 100 * n() / nrow(netflix), total = n())
hbo %>% 
  group_by(type) %>% summarise(percent = 100 * n() / nrow(hbo), total = n())
amazon %>% 
  group_by(type) %>% summarise(percent = 100 * n() / nrow(amazon), total = n())
apple %>% 
  group_by(type) %>% summarise(percent = 100 * n() / nrow(apple), total = n())


```



# Votes comparison
```{r}
#imdb vs votes
all_titles %>% ggplot() + aes(imdb_score ,imdb_votes, color = type) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)
all_movies %>% ggplot() + aes(imdb_score ,imdb_votes) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)all_movies %>% ggplot() + aes(imdb_score ,imdb_votes) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)all_movies %>% ggplot() + aes(imdb_score ,imdb_votes) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)
all_shows  %>% ggplot() + aes(imdb_score ,imdb_votes) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)

#tmdb vs popularity
all_titles %>% ggplot() + aes(tmdb_score ,tmdb_popularity, color = type) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)
all_movies %>% ggplot() + aes(tmdb_score ,tmdb_popularity) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)
all_shows  %>% ggplot() + aes(tmdb_score ,tmdb_popularity) + geom_point(na.rm = T, position = 'jitter') + facet_wrap(~ platform)


all_titles %>% ggplot() + aes(tmdb_score ,imdb_score , color = type) + geom_density_2d(na.rm = T) + facet_wrap(~ platform)
all_movies %>% ggplot() + aes(tmdb_score ,imdb_score) + geom_density_2d(na.rm = T) + facet_wrap(~ platform)
all_shows  %>% ggplot() + aes(tmdb_score ,imdb_score, color = type) + geom_density_2d(na.rm = T)

```



```{r}

# imdb scores on each platform, who has higher scores and who has more lower scores
all_titles %>% filter(imdb_score > 5) %>% ggplot() + aes(imdb_score, fill = type) + geom_histogram(binwidth = 1/3)+facet_wrap(~ platform)
all_titles %>% filter(imdb_score > 5) %>% ggplot() + aes(imdb_score) + geom_histogram()+facet_wrap(~ type)

all_titles %>% filter(imdb_score < 5) %>% ggplot() + aes(imdb_score, fill = type) + geom_histogram(binwidth = 1/3)+facet_wrap(~ platform)
all_titles %>% filter(imdb_score < 5) %>% ggplot() + aes(imdb_score) + geom_histogram()+facet_wrap(~ type)
# note decide whether or not to use all scores and scores that are above average or just scores above average and below average
all_shows %>% ggplot() + aes(imdb_score, fill = platform) + geom_histogram()+facet_wrap(~ platform)
all_titles %>% ggplot() + aes(imdb_score, fill = 'red') + geom_histogram()+facet_wrap(~ type)
```


```{r}
#tmbd
all_titles %>% filter(tmdb_score > 5) %>% ggplot() + aes(tmdb_score, fill = type) + geom_histogram()+facet_wrap(~ platform)
all_titles %>% filter(tmdb_score > 5) %>% ggplot() + aes(tmdb_score) + geom_histogram()+facet_wrap(~ type)

all_titles %>% ggplot() + aes(tmdb_score, fill = platform) + geom_histogram()+facet_wrap(~ type)

all_movies %>% ggplot() + aes(tmdb_score, fill = platform) + geom_histogram()+facet_wrap(~ platform)

```
# Other things to look at
 - 
 - release dates vs score and popularity
 - popularity and score vs age
 - 
```{r}
#graph by total
all_totals %>% 
  ggplot(aes(platform,total, fill = type)) + geom_bar(stat ="identity", position = "dodge") + geom_text(aes(label = total), vjust = -0.5, size = 3, position=position_dodge(1))



#imdb vs votes
all_titles %>% ggplot() + aes(imdb_score ,imdb_votes, color = type) + geom_density_2d( alpha = .4, na.rm = T, position = 'jitter') + facet_wrap(~ platform)+scale_y_log10()
#tmdb vs popularity
all_titles %>% ggplot() + aes(tmdb_score ,tmdb_popularity, color = type) + geom_density_2d( alpha= .4, na.rm = T, position = 'jitter') + facet_wrap(~ platform) + scale_y_log10()


#tmbd
all_titles %>% ggplot() + aes(tmdb_score, fill = type) + geom_density(alpha = 0.4)+facet_wrap(~ platform)

#imdb
all_titles %>% ggplot() + aes(imdb_score, fill = type) + geom_density(alpha = 0.4) +facet_wrap(~ platform)

d3 = all_genres %>% filter(type == 'MOVIE') %>% ggplot(aes(reorder(genres, popularity), popularity))+ geom_bar(stat ="identity") + coord_flip()+ facet_wrap(~type)
d4 = all_genres %>% filter(type == 'SHOW') %>% ggplot(aes(reorder(genres, popularity), popularity))+ geom_bar(stat ="identity") + coord_flip()+ facet_wrap(~type)
grid.arrange(d3,d4, ncol = 2)


all_shows %>% separate_rows(genres, sep = ",") %>% filter(!is.na(imdb_score), genres != "") %>% ggplot(aes(genres, imdb_score))+ geom_bar(stat ="identity")+ coord_flip()

all_movies %>% separate_rows(genres, sep = ",") %>% filter(!is.na(imdb_score), genres != "") %>% ggplot(aes(genres, imdb_score))+ geom_bar(stat ="identity")+ coord_flip()

all_genres =all_titles %>% 
  separate_rows(genres, sep = ",") %>% filter(!is.na(imdb_votes), genres != "")%>% group_by(genres, type) %>% summarise(popularity = weighted.mean(imdb_votes, imdb_votes), total = n(),  .groups = 'drop')

all_titles %>% separate_rows(genres, sep = ",")%>% filter(genres %in% c("drama", "comedy", "thriller", "animation")) %>%  arrange(desc(imdb_score)) %>% group_by(genres ) %>% summarise(most_popular = head(title, 3), type = first(type), ) 

 all_titles %>% filter( genres !="") %>% arrange(desc(imdb_score))%>% select(genres, title, platform) %>% head(10)
all_genres %>% ggplot(aes(genres, popularity)) + geom_bar(stat = 'identity') + coord_flip() + facet_wrap(~type)
all_genres %>% ggplot(aes(genres, popularity)) + geom_bar(stat = 'identity') + coord_flip() + facet_wrap(~type)
 
all_movies %>% separate_rows(genres, sep = ",") %>% filter(genres != "") %>% group_by(genres,type) %>% summarise(total = n(),  .groups = 'drop') %>% ggplot(aes(genres, total))+ geom_bar(stat ="identity", )+ coord_flip() + facet_wrap(~type)

all_shows %>% separate_rows(genres, sep = ",") %>% filter(genres != "") %>% group_by(genres,type) %>% summarise(total = n(),  .groups = 'drop') %>% ggplot(aes(genres, total))+ geom_bar(stat ="identity")+ coord_flip() + facet_wrap(~type)

avgcerts= all_titles %>% 
  filter(!is.na(imdb_score), age_certification != "")%>% group_by(age_certification, type) %>% summarise(rating = mean(imdb_score), total = n(),  .groups = 'drop')
avgcerts %>%
  filter(!is.na(age_certification)) %>% ggplot(aes(age_certification, rating, fill = type)) +  geom_bar(stat = "identity")
```
```


